From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-04-30 article/article.tex
figure tidied up
Real networks experiments

\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{color}

@@

\textbf{Non-overlapping modules.} Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with 1000 and 5000 nodes varying the mixing coefficient (number of edges between communities).
As one would expect, the prediction of the method drops off steeply where communities are less defined above a mixing coefficient of 0.6.
Using larger seed sets also improves accuracy with some prediction of true communities being possible at extremely high levels of mixing.

\textbf{Overlapping modules.} 
In figure \ref{fig:auc_overlap} we show the results of network performance when tested against an increasing level of overlapping communities.
For these tests we fix the mixing coefficient at $0.3$.
Here, each vertex can belong to up to 4 communities.
In order to test performance we varied the fraction of nodes that are in more than one community.
Interestingly, the method still has an AUC score above 0.5 when all nodes are placed in multiple communities.
This indicates that the method is capable of uncovering latent overlapping memberships even when given a relatively small number of seed nodes.

@@

@@

>>>>

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[]{}{}{}
\acmYear{2018}
\copyrightyear{2018}

\usepackage[utf8]{inputenc}
\usepackage{color}

@@

\subsubsection{Non-overlapping modules.}
Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with 1000 and 5000 nodes varying the mixing coefficient (number of edges between communities).
As one would expect, the prediction of the method drops off steeply where communities are less defined above a mixing coefficient of 0.6.
Using larger seed sets also improves accuracy with some prediction of true communities being possible at extremely high levels of mixing.

@@

\subsubsection{Overlapping modules.} 
In figure \ref{fig:auc_overlap} we show the results of network performance when tested against an increasing level of overlapping communities.
For these tests we fix the mixing coefficient at $0.3$.
Here, each vertex can belong to up to 4 communities.
In order to test performance we varied the fraction of nodes that are in more than one community.
Interestingly, the method still has an AUC score above 0.5 when all nodes are placed in multiple communities.
This indicates that the method is capable of uncovering latent overlapping memberships even when given a relatively small number of seed nodes.

@@

\subsubsection{Cluster significance}
In this section we evaluate the method for testing labels to discover significant communities by comparing the scores to randomly selected communities.
In order to do this, we
